Use and acquisition of causal information for decision making under uncertainty

### 2018-05-10 Segundo_Semestre/CausalML_Workshop/Extended_Abstract.tex
cambios en la intro y related work segun correcciones de hugo

\section{Introduction}
A fundamental part of intelligent reasoning (\cite{lake2017building}, \cite{danks2014unifying}) is being able to make decisions under uncertain conditions. In some cases, a decision maker has enough information about his environment to make choices by calculating expected utilities.

In other cases she may not have enough information to proceed in this way. One possible way is to try to \textit{learn} that missing information from the environment by interacting with it.

We consider the case where the uncertain environment is governed by a \textit{causal mechanism} unknown to the agent.

Human beings are known to learn causal graphical models in sequential decision making processes (\cite{sloman2006causal}, \cite{nichols2007decision}, \cite{meder2010observing}, \cite{hagmayer2013repeated}, \cite{danks2014unifying}), although this learning is not perfect (\cite{rottman2014reasoning}).

Learning by interaction has been extensively studied in Reinforcement Learning \cite{sutton1998reinforcement}, but the most common used techniques are purely reactive (\cite{garnelo2016towards}) and do not consider any structure of the environment such as causal relations.

\section{Related Work}
One stage decision problems in which the decision maker will choose one action, and one action only, and then observe the consequences of it have been modelled as \textit{bandit problems}.

>>>>

\section{Introduction}
A fundamental part of intelligent reasoning (\cite{lake2017building}, \cite{danks2014unifying}) is being able to make decisions under uncertain conditions. In some cases, a decision maker who faces an uncertain environment has enough information to make choices by maximizing expected utilities.  If enough information is not available, the decision maker could try to \textit{learn} from the environment by interacting with it.

Learning by interaction has been extensively studied in Reinforcement Learning \cite{sutton1998reinforcement}, but the most common used techniques are purely reactive (\cite{garnelo2016towards}) and do not consider any structure of the environment.

In this paper we consider the case where the uncertain environment is governed by a \textit{causal mechanism} unknown to the agent. Since human beings are known to learn causal graphical models in sequential decision making processes (\cite{sloman2006causal}, \cite{nichols2007decision}, \cite{meder2010observing}, \cite{hagmayer2013repeated}, \cite{danks2014unifying}), although this learning is not perfect (\cite{rottman2014reasoning}), we propose that an autonomous agent can learn and use causal information while interacting with an uncertain environment.

We model the interaction between the decision maker and his environment a repeated game with incomplete information between a player called Nature whi selects his actions from the causal model and the decision maker.

\section{Related Work}
Consider a one stage decision problem where the relation between actions and consequences is given by a causal model, \cite{lattimoreNIPS2016} analyzes this situation as a \textit{bandit problem}.
